---
title: "Tallgrass Restoration Legacies, Summary"
author: "Beau Larkin"
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    df_print: tibble
    fig_caption: yes
    highlight: tango
    toc: true
    toc_depth: 2
geometry: margin = 0.5in
fontsize: 12
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, tidy = TRUE, message = FALSE, warning = FALSE)
```

# Packages

```{r libraries, echo = TRUE}
packages_needed = c("tidyverse",
                    "png",
                    "knitr",
                    "conflicted",
                    "formatR")
packages_installed = packages_needed %in% rownames(installed.packages())
if (any(!packages_installed)) {
    install.packages(packages_needed[!packages_installed])
    }
for (i in 1:length(packages_needed)) {
    library(packages_needed[i], character.only = T)
}
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
```

# Description
The goal is to present results and discuss whether a path forward exists. If so, we will determine
the strategy that presents the best story, organization, and interpretation of these results. 

# Data
For this summary, I'll pull as many objects as possible from existing files to reduce the number of 
interspersed code chunks. A few quick new analyses will be necessary, though. Data are loaded here. 

```{r data, echo = TRUE}
sites <- read_csv(paste0(getwd(), "/clean_data/sites.csv"), show_col_types = FALSE) %>%
    mutate(field_type = factor(field_type,ordered = TRUE, levels = c("corn", "restored", "remnant")),
           yr_since = replace(yr_since, which(field_type %in% c("remnant", "corn")), NA)) %>%
    select(-lat, -long, -yr_restore, -yr_rank) %>% 
    arrange(field_key)
```



recall this for code chunk options: https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf